Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-07-31 TEX/draft_biology.tex
morning session

We represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$ where $k \geq 0, q \geq 1$ are integers~\cite{landa2017steerable}. As we demonstrate below, this makes it easier to account for the fact that all in-plane rotations of the micrographs are equally likely observations. This is only a concern for the second and third order autocorrelations. Below, we start with $p=2$.
The PSWFs are eigenfunctions of the truncated Fourier transform and are given in polar coordinates by
\begin{align}
	\psi_{k,q}(r,\varphi) & = \left\{\begin{array}{ll} \frac{1}{\sqrt{8\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \label{eq:prolatesdef}
\end{align}
where the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are \TODO{real?} scaling factors which will be defined in the next section.
The PSWFs are orthonormal on the unit disk.

For $\Bell \in [-(P-1), P-1]^2$, let us define 
\[\begin{aligned} 
\mathfrak{a}^2[k, q] & =
\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{aligned}\]
where $\psi_{k,q}[\Bell] \triangleq \psi_{k,q}(\Bell/P)$ \TODO{?} is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
Knowledge of these coefficients is essentially equivalent to knowledge of the second-order correlations owing to the following approximate identity:
\begin{align}
 a^2_\II[\mb i] & \approx \sum_{k,q}\mathfrak{a}^2[k,q]\psi_{k,q}[\Bell].
 \label{eq:approxprolatesdiscrete}
\end{align}
We now proceed to show that the coefficients $\mathfrak{a}^2[k, q]$ can be computed from the micrographs directly.

By definition,
\begin{align}
\mathfrak{a}^2[k,q] & =\sum_{\Bell} a^2_\II[\Bell] \overline{\psi_{k,q}[\Bell]} \nonumber\\
	& = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}[\Bell]}\right) \nonumber \\
	& = \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k,q}[\mb i], \label{eq:frakatwo}
\end{align}
where we defined
\begin{align*}
	a_{k,q}[\mb i] & = \sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}[\Bell]}.
\end{align*}
These coefficients can be computed efficiently. Indeed, consider a patch of the micrograph $\II$ centered around pixel $\mb i$ and of size $(2P-1) \times (2P-1)$. This is exactly the patch indexed in the sum above. Hence, using the same approximation as we did in~\eqref{eq:approxprolatesdiscrete}, a direct expansion of that patch in the discretized PSWFs yields the sought coefficients:
\begin{align}
	\II[\mb i+\Bell] & \approx \sum_{k,q} a_{k,q}[\mb i] \psi_{k,q}[\Bell]. \label{eq:itamar}
\end{align}
%Considering equation~\eqref{eq:frakatwo}, our main task is to compute the coefficients $a_{k,q}$, which from the equation above can be done as follows: 
Thus, we proceed as follows:
for each position $\mb i$ in the micrograph $\II$, we extract the corresponding patch of size $2P-1$, expand it in the discretized PSWFs as in~\eqref{eq:itamar}, and collect the $a_{k,q}$ as per~\eqref{eq:frakatwo} to constitute the second-order autocorrelation of the micrograph.

Crucially, following this formalism, it is now straightforward to account for all in-plane rotations (and reflections) of the micrograph. Indeed, as can be seen from the definition of the (continuous) PSWFs~\eqref{eq:prolatesdef}, the effects of rotations and reflections on expansion coefficients of real images are, respectively, phase modulation and conjugation. By analogy in the discrete case, we have the following approximate expansions for a patch rotated about its center $\mb i$ by an angle $\alpha$:
\[ \II^{\alpha,+}[\mb i+\Bell] = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}[\Bell],\]
and the reflection followed by a rotation by angle $\alpha$:
\[ \II^{\alpha,-}[\mb i+\Bell] = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}[\Bell].\]
%where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
\[\begin{aligned} 
\mathfrak{a}^2[k,q] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}[\mb i] +
\overline{a_{k,q}}[\mb i]]e^{-ik\alpha}\, d\alpha\right)\\ 
&= \delta[k] \frac{1}{N^2}\sum_{\mb i}\II[\mb i]a_{0,q}[\mb i], \end{aligned}\]
where in the last equality we used that both $\II$ and $\psi_{0,q}$ are real valued.
Thus, the second-order autocorrelation, though two-dimensional, effectively only provides one-dimensional information.

We now follow a similar approach to estimate the bias term $b_2$.
Introduce the coefficients $\mathfrak{b}_2$ as: \TODO{We're using that $R$ functions are zero at the origin for $k\neq 0$, right? We didn't introduce that fact so far.}
\[\begin{aligned} 
\mathfrak{b}_2[k,q] & = \sigma^2\sum_{\Bell}\delta[\Bell]\overline{\psi_{k,q}}[\Bell]\\
&= \sigma^2\overline{\psi_{k,q}}[\mb 0]\\
&= \delta[k] \frac{\sigma^2}{\sqrt{2\pi}}R_{0,q}(0). \end{aligned}\]
With this definition, we have the usual approximation:
\[ b_2[\Bell] = \sigma^2\delta[\Bell] \approx \sum_{k,q}\mathfrak{b}_2[k,q]\psi_{k,q}[\Bell].\]

We then estimate the expansion coefficients of the clean power spectrum as
\[ \widetilde{\mk m_2}(k,q) = \mk m_2(k,q) - \mk b_2(k,q).\]

\TODO{---------------------------------------------}

, which we use to include all in-plane rotations of the projections in the micrograph to compute the autocorrelations, and compute only the blocks on the diagonal - see . 
The PSWFs are eigenfunctions of the truncated Fourier transform and satisfy 
\be\label{eq:PSWF_defn_eq}
\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
\ee
given in polar coordinates by
\[ \psi_{k,q}(r,\varphi) = \left\{\begin{array}{ll} \frac{1}{2\sqrt{2\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \quad k\geq 0,\ q\geq 1,\]
and are orthonormal on the unit disc.\footnote{In \cite{landa2017steerable}, PSWFs are defined as $2\psi_{k,q}/\alpha_{k,q}$, but using the above definition simplifies the formula for the expansion coefficients.}

The micrograph autocorrelations are given by an average over the particle orientations.
Since the specific in-plane rotation of each projection is equally likely to appear, we would like to   consider all possible in-plane rotations. 
This can be done efficiently using steerable bases , a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients;  \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}.

The clean autocorrelations $\gamma\langle m_k[I_{\omega}]\rangle_{\omega}$ which we estimate from the micrograph are given by an average over the particule orientations. In particular, they are invariant under in-plane rotations of the projections, and can therefore be block-diagonalized in any steerable basis, a basis in which an in-plane rotation corresponds to a phase shift of the expansion coefficients - see \cite{bhamre2016denoising,landa2017steerable,zhao2016fast}. For this paper, we represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$, which we use to include all in-plane rotations of the projections in the micrograph to compute the autocorrelations, and compute only the blocks on the diagonal - see \cite{landa2017steerable}.

The PSWFs are eigenfunctions of the truncated Fourier transform and satisfy \TODO{approximate} \TODO{generate the Gram matrix of the discrete approximation}
\be\label{eq:PSWF_defn_eq}
\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
\ee
given in polar coordinates by
\[ \psi_{k,q}(r,\varphi) = \left\{\begin{array}{ll} \frac{1}{2\sqrt{2\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \quad k\geq 0,\ q\geq 1,\]
and are orthonormal on the unit disc.\footnote{In \cite{landa2017steerable}, PSWFs are defined as $2\psi_{k,q}/\alpha_{k,q}$, but using the above definition simplifies the formula for the expansion coefficients.}

The mean is a scalar and is already invariant under in-plane rotations of the projections in the dataset, since all projections have the same mean $Lm_1[\phi]$, as explained above. For the power spectrum, we expand it as
\[ m_2[\II](\Delta\mb i) =
\sum_{k,q}\mathfrak{m}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
where the expansion is truncated according to the rule in~\cite{landa2017steerable}, and obtain the expansion coefficients as
\[\begin{aligned} 
\mathfrak{m}_2(k,q) &=
\sum_{\Delta\mb i}m_2[\II](\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
&=
\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i}\II(\mb i+\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\right)\\
&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{k,q}(\mb i), \end{aligned}\]
where we note that if we expand a patch of size $(2L-1) \times (2L-1)$ centered about $\II(\mb i)$ in PSWFs as
\[ \II(\mb i + \Delta\mb i) = \sum_{k,q}a_{k,q}(\mb i)\psi_{k,q}(\Delta\mb i),\quad ||\Delta\mb i||_{\infty}\leq L-1,\]
the expansion coefficients are given by the inner product
\[ a_{k,q}(\mb i) = \sum_{\Delta\mb i}\II(\mb i + \Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}.\]
As shown in \cite{landa2017steerable, zhao2016fast}, the rotation of the above patch by an angle $\alpha$ is given by
\[ \II^{\alpha,+}(\mb i+\Delta\mb i) = \sum_{k,q}a_{k,q}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
and the reflection of that disc rotated by an angle $\alpha$ by
\[ \II^{\alpha,-}(\mb i+\Delta\mb i) = \sum_{k,q}\overline{a_{k,q}}e^{-ik\alpha}\psi_{k,q}(\Delta\mb i),\]
where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB. Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
\[\begin{aligned} 
\mathfrak{m}_2(k,q) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}[a_{k,q}(\mb i) +
\overline{a_{k,q}}(\mb i)]e^{-ik\alpha}\, d\alpha\right)\\ 
&= \delta_{k,0} \frac{1}{L^2}\sum_{\mb i}\II(\mb i)a_{0,q}(\mb i), \end{aligned}\]
where in the last equality we dropped the real part since both
$\II$ and $\psi_{0,q}$ are real valued.
Thus, the average power spectrum is effectively a vector. To estimate the clean power spectrum coefficients, we also expand the bias term in PSWFs. Writing
\[ b_2(\Delta\mb i) = \sigma^2\delta(\Delta\mb i) = \sum_{k,q}\mathfrak{b}_2(k,q)\psi_{k,q}(\Delta\mb i),\]
the coefficients are given by
\[\begin{aligned} 
\mathfrak{b}_2(k,q) &= \sigma^2\sum_{\Delta\mb i}\delta(\Delta\mb i)\overline{\psi_{k,q}(\Delta\mb i)}\\
&= \sigma^2\overline{\psi_{k,q}(\mb 0)}\\
&= \frac{\sigma^2}{\sqrt{2\pi}}R_{0,q}(0). \end{aligned}\]
We then estimate the expansion coefficients of the clean power spectrum as
\[ \widetilde{\mk m_2}(k,q) = \mk m_2(k,q) - \mk b_2(k,q).\]

We expand the bispectrum as
\[ m_3[\II](\Delta \mb i_1, \Delta \mb i_2) = \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{m}_3(k_1,q_1;k_2,q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
The expansion coefficients are then given by
\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \sum_{\Delta\mb i_1, \Delta\mb i_2}m_3[\II](\Delta\mb i_1,\Delta\mb i_2)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\psi_{k_2,q_2}(\Delta\mb i_2)\\
&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\sum_{\Delta\mb i_1}\II(\mb i+\Delta\mb i_1)\overline{\psi_{k_1,q_1}(\Delta\mb i_1)}\right)\left(\sum_{\Delta\mb i_2}\II(\mb i+\Delta\mb i_2)\psi_{k_2,q_2}(\Delta\mb i_2)\right)\\
&= \frac{1}{L^2}\sum_{\mb i}\II(\mb i) a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}.
\end{aligned}\]
Averaging over all rotations of $\II$ and its reflection, we obtain
\[\begin{aligned} \mathfrak{m}_3(k_1,q_1;k_2,q_2) &= \frac{1}{L^2}\sum_{\mb i}\II(\mb i)\left(\frac{1}{4\pi}\int_0^{2\pi}\left[a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)} + \overline{a_{k_1,q_1}(\mb i)}a_{k_2,q_2}(\mb i)\right]e^{-i(k_1-k_2)\alpha}d\alpha\right),\\
&= \delta_{k_1,k_2}\frac{1}{L^2}\sum_{\mb i}\II(\mb i)\Re\{a_{k_1,q_1}(\mb i)\overline{a_{k_2,q_2}(\mb i)}\}.\end{aligned}\]
Thus, the bispectrum in our steerable basis $\mathfrak{m}_3(k_1,q_1;k_2,q_2)$ is block-diagonal, and is effectively a 3-tensor.
Similarly to the power spectrum, we also expand the bias term in PSWFs as
\[ b_3(\Delta\mb i_1, \Delta\mb i_2) =  \gamma\sigma^2Lm_1[\phi]\Big(\delta(\Delta\mb i_1 - \Delta\mb i_2) +
\delta(\Delta\mb i_1) + \delta(\Delta\mb i_2)\Big) = \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
b_3(k_1,q_1; k_2, q_2)\psi_{k_1,q_1}(\Delta\mb i_1)\overline{\psi_{k_2,q_2}(\Delta\mb i_2)},\]
where the coefficients are given by
\[ \mk b_3(k_1,q_1; k_2,q_2) = \gamma\sigma^2L m_1[\phi]\delta_{k_1,k_2}\left[\delta_{q_1,q_2} + \delta_{k_1,0}\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right]. \]

@@

>>>>

We represent our autocorrelations using Prolate Spheroidal Wave Functions (PSWFs) $\{\psi_{k,q}\}$ where $k \geq 0, q \geq 1$ are integers~\cite{slepian1964pswfIV}. As we demonstrate below, this makes it easier to account for the fact that all in-plane rotations of the micrographs are equally likely observations. This is only a concern for the second and third order autocorrelations. Below, we start with $p=2$.
The PSWFs are eigenfunctions of the truncated Fourier transform and are given in polar coordinates by
\begin{align}
	\psi_{k,q}(r,\varphi) & = \left\{\begin{array}{ll} \frac{1}{\sqrt{8\pi}}\alpha_{k,q}R_{k,q}(r)e^{\iota k\varphi}, & r\leq 1,\\ 0, & r>1,\end{array}\right. \label{eq:prolatesdef}
\end{align}
where the ${R_{k,q}}$ are a family of real, one-dimensional functions and the ${\alpha_{k,q}}$ are \TODO{real?} scaling factors which will be defined in the next section.
The PSWFs are orthonormal \TODO{orthogonal?} on the unit disk.

For $\Bell \in [-(P-1), P-1]^2$, let us define 
\[\begin{aligned} 
\mathfrak{a}^2[k, q] & =
\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{aligned}\]
where $\psi_{k,q}[\Bell] := \psi_{k,q}(\Bell/(P-1))$ is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
Knowledge of these coefficients is essentially equivalent to knowledge of the second-order correlations owing to the following approximate identity:
\begin{align}
 a^2_\II[\Bell] & \approx \sum_{k,q}\mathfrak{a}^2[k,q]\psi_{k,q}[\Bell].
 \label{eq:approxprolatesdiscrete}
\end{align}
This holds because the continuous PSWFs form an orthogonal basis, and their discretized counterparts are (empirically) almost orthogonal. As a result, for our purposes, the pair of equations above provides a basis expansion for the autocorrelations.

We now proceed to show that the coefficients $\mathfrak{a}^2[k, q]$ can be computed from the micrographs directly.
By definition,
\begin{align}
\mathfrak{a}^2[k,q] & =\sum_{\Bell} a^2_\II[\Bell] \overline{\psi_{k,q}[\Bell]} \nonumber\\
	& = \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}[\Bell]}\right) \nonumber \\
	& = \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k,q}[\mb i], \label{eq:frakatwo}
\end{align}
where we defined
\begin{align}
	a_{k,q}[\mb i] & = \sum_{\Bell}\II[\mb i+\Bell]\overline{\psi_{k,q}[\Bell]}.
	\label{eq:patchcoefficients}
\end{align}
These coefficients can be computed efficiently. Indeed, consider a patch of the micrograph $\II$ centered around pixel $\mb i$ and of size $(2P-1) \times (2P-1)$. This is exactly the patch indexed in the sum above. Hence, using the same approximation as we did in~\eqref{eq:approxprolatesdiscrete}, a direct expansion of that patch in the discretized PSWFs yields the sought coefficients:
\begin{align}
	\II[\mb i+\Bell] & \approx \sum_{k,q} a_{k,q}[\mb i] \psi_{k,q}[\Bell]. \label{eq:itamar}
\end{align}
%Considering equation~\eqref{eq:frakatwo}, our main task is to compute the coefficients $a_{k,q}$, which from the equation above can be done as follows: 
Thus, we proceed as follows:
for each position $\mb i$ in the micrograph $\II$, we extract the corresponding patch of size $2P-1$, expand it in the discretized PSWFs as in~\eqref{eq:itamar}, and collect the $a_{k,q}$ as per~\eqref{eq:frakatwo} to constitute the second-order autocorrelation of the micrograph.

Crucially, following this formalism, it is now straightforward to account for all in-plane rotations and reflections of the micrograph. Indeed, as can be seen from the definition of the (continuous) PSWFs~\eqref{eq:prolatesdef}, the effects of rotations and reflections on expansion coefficients of real images are, respectively, phase modulation and conjugation: this is why this the PSWF basis is called \emph{steerable}~\cite{landa2017steerable,zhao2016fast}. By analogy in the discrete case, we have the following approximate expansions for a patch rotated about its center $\mb i$ by an angle $\alpha$:
\[ \II^{\alpha,+}[\mb i+\Bell] \approx \sum_{k,q}a_{k,q}e^{-\iota k\alpha}\psi_{k,q}[\Bell],\]
and the reflection followed by a rotation by angle $\alpha$:
\[ \II^{\alpha,-}[\mb i+\Bell] \approx \sum_{k,q}\overline{a_{k,q}}e^{-\iota k\alpha}\psi_{k,q}[\Bell].\]
%where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
\[\begin{aligned} 
\mathfrak{a}^2[k,q] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k,q}[\mb i] +
\overline{a_{k,q}}[\mb i]\right)e^{-\iota k\alpha}\, d\alpha\right)\\ 
&= \delta[k] \frac{1}{N^2}\sum_{\mb i}\II[\mb i]a_{0,q}[\mb i], \end{aligned}\]
where in the last equality we used that $a_{0,q}[\mb i]$ is real since both $\II$ and $\psi_{0,q}$ are real valued (more generally, $a_{-k,q}=\overline{a_{k,q}}$).
Thus, the second-order autocorrelation, though two-dimensional, effectively only provides radial information.

We now follow a similar approach to estimate the bias term $b_2$.
Introduce the coefficients $\mathfrak{b}_2$ as:
\[\begin{aligned} 
\mathfrak{b}_2[k,q] & = \sigma^2\sum_{\Bell}\delta[\Bell]\overline{\psi_{k,q}}[\Bell]\\
&= \sigma^2\overline{\psi_{k,q}}[\mb 0]\\
&= \delta[k] \frac{\sigma^2}{\sqrt{2\pi}}R_{0,q}(0), \end{aligned}\]
where we used the fact that the functions $R_{k,q}$ are zero at the origin for $k\neq 0$.
With this definition, we have the usual approximation:
\[ b_2[\Bell] = \sigma^2\delta[\Bell] \approx \sum_{k,q}\mathfrak{b}_2[k,q]\psi_{k,q}[\Bell].\]

We now turn out attention to the third order autocorrelation. Following the same lines, we define the coefficients:
\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \sum_{\Bell_1, \Bell_2} a^3_\II[\Bell_1,\Bell_2]\overline{\psi_{k_1,q_1}[\Bell_1]}\psi_{k_2,q_2}[\Bell_2]\\
&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right)\left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]},
\end{aligned}\]
where the patch expansion coefficients $a_{k,q}$ are as defined in~\eqref{eq:patchcoefficients}.
The coefficients $\mathfrak{a}^3[k_1,q_1;k_2,q_2]$ are related to the third-order autocorrelation via the approximate identity:
\[ a^3_\II[\Bell_1, \Bell_2] \approx \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{a}^3[k_1,q_1;k_2,q_2]\psi_{k_1,q_1}[\Bell_1]\overline{\psi_{k_2,q_2}[\Bell_2]}.\]
Averaging over all rotations of $\II$ and its reflection, we obtain
\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right),\\
&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}.\end{aligned}\]
Thus, similarly to the second-order autocorrelation, averaging over all in-plane rotations reveals that the 4-D third-order autocorrelation truly only carries information along three dimensions.

Finally, we treat the bias terms, using approximate orthonormality \TODO{!} of the discretized PSFWs:
\[ \mk b_3[k_1,q_1; k_2,q_2] = \gamma\sigma^2\langle a^1_{I_{\omega}} \rangle_\omega \delta[k_1 - k_2]\left[\delta[q_1-q_2] + \delta[k_1]\frac{1}{2\pi}(\alpha_{0,q_1} + \alpha_{0,q_2})R_{0,q_1}(0)R_{0,q_2}(0)\right]. \]
Thus,
\begin{align*}
	b_3[\Bell_1, \Bell_2] & = \gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
	\delta[\Bell_1] + \delta[\Bell_2]\Big) \\
	& \approx \sum_{\substack{k_1, q_1\\ k_2, q_2}} \mk 
	b_3[k_1,q_1; k_2, q_2]\psi_{k_1,q_1}[\Bell_1]\overline{\psi_{k_2,q_2}[\Bell_2]}.
\end{align*}

@@

\TODO{===}

\be\label{eq:PSWF_defn_eq}
\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
\ee

\TODO{===}
